### 2016-08-02 Theorem2_FP.tex
comments on theorem 2

\fixme{Clean up to match style, language and typesetting (macros,
  especially) of previous theorem.}

Let $B_{\mathrm{ds}}=(\Hash,\Rep,\Qry)$ be the hash-based filter defined as earlier, except the hash functions are defined as $h_j(x) = \FK, \, j \in [1,k]$. Informally, the following result shows, if F is PRF secure and the filter has low FP-error in the non-adaptive setting, then $B_{\mathrm{ds}}$ is secure against adaptive FP-finding adversaries.

\begin{theorem}\label{thm2}
Fix $k,m,n >0$. Let $B_{\mathrm{ds}}$ be the hash based filter described earlier. If there exists an adaptive adversary $A$ compatible with $\ExpFPPubHash{B_{\mathrm{ds},t}}{\cdot}$ asking $q \times r$ queries in $t$ time, then there exists an adversary $B$ attacking the PRF game in time $O(t)$ and asking same number of queries as $A$ such that 
\begin{equation}
\AdvFPSecHash{B_\mathrm{ds},t}{A}\leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\end{equation}
\end{theorem}

\acnote{I think we should give a proof of the non-adaptive FP-error bound $(1-e^{-kn/m})^k + O(1/n) $. This bound which we picked from KM's theorem 6.2, is a particular case (double hashing scheme).  Theorem 6.1, on the other hand holds good for any hashing scheme that satisfies Lemma 4.1. \\
 I tried to give the FP-bound as a Lemma. 
\begin{lemma}\label{lemma1}
Fix $k,m,n >0$. The FP-error of hash-based filter $B_{\mathrm{ds}}$ with hash functions $h_j(x) = \FK, \, j \in [k]$ is upperbounded by $(1-e^{-kn/m})^k + O(1/n)$.
\end{lemma}
}
\acnote{As I had told you earlier, I was not able to understand the proofs of KM paper and now I am stuck in this proof. 
\begin{proof}($Lemma$ \ref{lemma1})
In \ref{KM}, $Theorem \,6.1$ gives the upperbound of FP error of any hashing scheme satisfying the 5 conditions enlisted in Lemma 4.1, and all these conditions are satisfied by $B_{\mathrm{ds}}$ as shown below.\\
Since the hash functions of $B_{\mathrm{ds}}$ provide randomness with domain separation and the number of hash functions are controlled by parameter $j$, condition 1 and 2 are trivially satisfied. The last condition is also trivial, since size of $B_{\mathrm{ds}}$ will be some constant multiple of size of $S$, as in the classical bloom filter.\\
The satisfiability of remaining 2 conditions is non-trivial ...
\end{proof}}
%
\begin{proof}[\Cref{thm2}]
We use a game playing argument similar to \Cref{thm1} to prove this theorem. In \game{0}(A), adversary attacks the FP game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpFPSecHash{B_\mathrm{ds},r}{A}$.
\begin{equation}
\AdvFPSecHash{B_\mathrm{ds},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0T2}
\end{equation}
\noindent
\game{1}(A), \game{2}(A), and \game{3}(A) are same as in the previous theorem, except the hash-functions are distinct random functions. The non-adaptive counterparts of $B_\mathrm{ds}$ as well as the prf adversary are  identical to those of $B_\mathrm{lin}$. As shown in \game{1}(A) and \game{2}(A), the $\HashOracle$ oracle returns distinct random values in these simulations. $B$, on the other hand uses its oracle to generate random values (for $b=0$) in the following way, $h_j(x) = \calO(\langle j,x \rangle)$.

>>>>

Let $B_{\mathrm{ds}}=(\Hash,\Rep,\Qry)$ be the hash-based filter defined as earlier, except the hash functions are defined as $h_j(x) = \FK, \, j \in [1,k]$. Informally, the following result shows, if~$F$ is PRF secure and the filter has low FP-error in the non-adaptive setting, then $B_{\mathrm{ds}}$ is secure against adaptive FP-finding adversaries.

\tsnote{Clean up so it looks like the previous theorem.}
\begin{theorem}\label{thm2}
Fix $k,m,n >0$. Let $B_{\mathrm{ds}}$ be the hash based filter described earlier. If there exists an adaptive adversary $A$ compatible with $\ExpFPPubHash{B_{\mathrm{ds},t}}{\cdot}$ asking $q \times r$ queries in $t$ time, then there exists an adversary $B$ attacking the PRF game in time $O(t)$ and asking same number of queries as $A$ such that 
\begin{equation}
\AdvFPSecHash{B_\mathrm{ds},t}{A}\leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\end{equation}
\end{theorem}

\tsnote{I don't see why this is necessary.  Doesn't it follow from the
standard bounds on Bloom filters (go look them up and adjust the
theorem accordingly) which assume that the hash functions are random
functions?  Whatever argument you use in Theorem 1 to justify
independence, i.e. turning one non-adaptive FP into~$r$ non-adaptive
FPs, should apply here, too.}
\acnote{I think we should give a proof of the non-adaptive FP-error bound $(1-e^{-kn/m})^k + O(1/n) $. This bound which we picked from KM's theorem 6.2, is a particular case (double hashing scheme).  Theorem 6.1, on the other hand holds good for any hashing scheme that satisfies Lemma 4.1. \\
 I tried to give the FP-bound as a Lemma. 
\begin{lemma}\label{lemma1}
Fix $k,m,n >0$. The FP-error of hash-based filter $B_{\mathrm{ds}}$ with hash functions $h_j(x) = \FK, \, j \in [k]$ is upperbounded by $(1-e^{-kn/m})^k + O(1/n)$.
\end{lemma}
}
\acnote{As I had told you earlier, I was not able to understand the proofs of KM paper and now I am stuck in this proof. 
\begin{proof}($Lemma$ \ref{lemma1})
In \ref{KM}, $Theorem \,6.1$ gives the upperbound of FP error of any hashing scheme satisfying the 5 conditions enlisted in Lemma 4.1, and all these conditions are satisfied by $B_{\mathrm{ds}}$ as shown below.\\
Since the hash functions of $B_{\mathrm{ds}}$ provide randomness with domain separation and the number of hash functions are controlled by parameter $j$, condition 1 and 2 are trivially satisfied. The last condition is also trivial, since size of $B_{\mathrm{ds}}$ will be some constant multiple of size of $S$, as in the classical bloom filter.\\
The satisfiability of remaining 2 conditions is non-trivial ...
\end{proof}}
%
\begin{proof}[\Cref{thm2}]
We use a game playing argument similar to \Cref{thm1} to prove this theorem. In \game{0}(A), adversary attacks the FP game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpFPSecHash{B_\mathrm{ds},r}{A}$.
\begin{equation}
\AdvFPSecHash{B_\mathrm{ds},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0T2}
\end{equation}
\noindent
\game{1}(A), \game{2}(A), and \game{3}(A) are same as in the previous theorem, except the hash-functions are distinct random functions. The non-adaptive counterparts of $B_\mathrm{ds}$ as well as the prf adversary are  identical to those of $B_\mathrm{lin}$. As shown in \game{1}(A) and \game{2}(A), the $\HashOracle$ oracle returns distinct random values in these simulations. $B$, on the other hand uses its oracle to generate random values (for $b=0$) in the following way, $h_j(x) = \calO(\langle j,x \rangle)$.
